%-------------------------
% Resume in Latex
% Author : Geet Purohit
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\ifdefined\pdfgentounicode\input{glyphtounicode}\fi

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.45in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable (pdflatex only)
\ifdefined\pdfgentounicode\pdfgentounicode=1\fi

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Geet Purohit} \\ \vspace{1pt}
    \small 973-814-0238 $|$ \href{mailto:geetp40@gmail.com}{\underline{geetp40@gmail.com}} $|$
    \href{https://linkedin.com/in/geetpurohit}{\underline{linkedin.com/in/geetpurohit}} $|$
    \href{https://github.com/geetpurohit}{\underline{github.com/geetpurohit}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Data Scientist III / Engineer III}{Nov. 2024 -- Present}
      {Verizon}{}
      \resumeItemListStart
        \resumeItem{Built churn models and an intervention simulator estimating the \textbf{incremental impact} of retention treatments (SMS, email, pricing/fee adjustments) on customer behavior, lifting internal decisioning coverage from \textbf{0\% to 60\%} and cutting outsourced engagement volume by \textasciitilde35\%.}
        \resumeItem{Architected a full-stack \textbf{credit-risk platform} that synthetically generates customer data to simulate credit-policy changes and their impact on bad-debt writeoff across \textbf{\$1.2B+ in exposure}, with zero production data.}
        \resumeItem{Led 2 explainable-AI (XAI) frameworks (Streamlit/Qlik) isolating real-time drivers of Verizon Gross Adds, cutting hypothesis-generation time \textbf{73\%} and presenting to \textbf{100+ stakeholders and executives}.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Scientist I}{Jan. 2023 -- Nov. 2024}
      {Verizon}{}
      \resumeItemListStart
        \resumeItem{Ran \textbf{K-Means segmentation} that surfaced 3 at-risk customer cohorts and shaped new retention campaigns, and built Tableau/BigQuery dashboards that eliminated \textbf{10+ hours} of weekly manual reporting.}
        \resumeItem{Automated serverless \textbf{time-series forecasting} for 9 value-segment consumer brands (Walmart, Tracfone, Straight Talk, FiOS), pioneering a 12-hour email-report system adopted across 3 organizations.}
        \resumeItem{Established a centralized data-science pipeline framework/API for Corporate Finance on GitLab, Domino Data Lab, and GCP, making cross-team collaboration \textbf{63\% more efficient}.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Engineering Intern}{Oct. 2021 -- Jun. 2022}
      {Human Genetics Institute of New Jersey}{}
      \resumeItemListStart
        \resumeItem{Trained \textbf{DeepLabCut} models for kinematic pose estimation on \textbf{1,000+} wet-lab experiments (Python, TensorFlow, CUDA) and shipped 4 IMARIS extensions automating 3D lesion reconstruction, making post-microscopy analysis \textbf{5x faster}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Persuade} $|$ \emph{Causal Inference, Heterogeneous Treatment Effects} $\cdot$ \href{https://geetpurohit.com/projects/uplift}{\underline{geetpurohit.com}}}{2026}
          \resumeItemListStart
            \resumeItem{Built a causal uplift model estimating \textbf{heterogeneous treatment effects} per customer with T-learner and X-learner meta-learners, quantifying the incremental lift of a treatment and validating it on the \textbf{Qini curve}, where accuracy is undefined for counterfactual targeting.}
            \resumeItem{Deployed it as a \textbf{zero-backend, in-browser app} that scores customers live and separates persuadables from sure things, lost causes, and sleeping dogs, directing treatment spend at the users a campaign actually moves.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Significance} $|$ \emph{A/B Test Design \& Analysis Toolkit} $\cdot$ \href{https://geetpurohit.com/projects/experiment}{\underline{geetpurohit.com}}}{2026}
          \resumeItemListStart
            \resumeItem{Built an interactive experimentation toolkit that \textbf{powers and sizes} an A/B test, then analyzes results with a two-proportion z-test and confidence interval, computed live in the browser.}
            \resumeItem{Demonstrated via Monte Carlo the two failure modes that invalidate most tests: \textbf{peeking} (false positives inflating past \textbf{25\%}) and skipping \textbf{CUPED} variance reduction (\textbf{\textasciitilde50\%} tighter estimates).}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{CreditLens} $|$ \emph{Explainable Credit-Risk Scorecard Engine} $\cdot$ \href{https://geetpurohit.com/projects/credit-risk}{\underline{geetpurohit.com}}}{2026}
          \resumeItemListStart
            \resumeItem{Built an end-to-end credit-default engine on \textbf{2.26M} LendingClub loans (weight-of-evidence binning, logistic scorecard, XGBoost/SHAP challenger; validated on ROC-AUC, KS, Gini, and calibration), deployed as a \textbf{zero-backend, in-browser app} with no target leakage.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Experimentation \& Causal Inference}{: A/B test design, quasi-experimental methods, uplift modeling, meta-learners (T/X-learner), heterogeneous treatment effects} \\
     \textbf{Languages}{: Python, SQL, R, Scala, Java, JavaScript/TypeScript} \\
     \textbf{ML}{: scikit-learn, XGBoost/LightGBM, PyTorch, TensorFlow, LLMs, MLflow} \\
     \textbf{Data, Cloud \& Viz}{: Apache Spark, GCP/BigQuery, Airflow, dbt, Docker, PostgreSQL, Tableau, Streamlit} \\
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{In Progress}
      {M.S. in Analytics, Computational Data Analytics Track}{}
    \resumeSubheading
      {Rutgers University}{Dec. 2022}
      {B.S. in Computer Science \& B.S. in Astrophysics, Minor in Mathematics, GPA: 3.7/4.0}{}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
